\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage[fleqn]{amsmath}
\usepackage{color}
\usepackage{lipsum}
\begin{document}
\setcounter{totalnumber}{5}
   \begin{flushright}
      \Large\textbf{Steven Murr}\\
      \large\textit{HW 11.2} \\
      \large\textit{Problems = \{ 1-5 all, 37\}}
   \end{flushright}
\begin{flushleft}
\makeatletter% Set distance from top of page to first float
\setlength{\@fptop}{5pt}
\makeatother

\setlength\parindent{0pt}1) Build a binary search tree for the words banana, peach, apple, pear, coconut, mango, and papaya using alphabetical order. \\
**See attached paper. \\
~\\
\setlength\parindent{0pt}2) Build a binary search tree for the words oenology, phrenology, campanology, ornithology, ichthyology, limnology, alchemy and astrology using alphabetical order. \\
**See attached paper. \\
~\\
\setlength\parindent{0pt}3) How many comparisons are needed to locate or to add each of these words in the search tree for Exercise 1, starting fresh each time? \\
\setlength\parindent{24pt}a) pear \\
\setlength\parindent{48pt} 3 - banana, peach, pear \\
\setlength\parindent{24pt}b) banana \\
\setlength\parindent{48pt} 1 - banana \\
\setlength\parindent{24pt}c) kumquat \\
\setlength\parindent{48pt} 4 - banana, peach, coconut, kumquat \\
\setlength\parindent{24pt}d) orange \\ 
\setlength\parindent{48pt} 5 - banana, peach, coconut, mango, orange \\
~\\
\setlength\parindent{0pt}4) How many comparisons are needed to locate or to add each of the words in the search tree for Exercise 2, starting fresh each time? \\
\setlength\parindent{24pt}a) palmistry \\
\setlength\parindent{48pt} 4 - oenology, phrenology, ornithology, palmistry \\
\setlength\parindent{24pt}b) etymology \\
\setlength\parindent{48pt} 6 - oenology, campanology, ichthyology, alchemy, astrology, etymology \\
\setlength\parindent{24pt}c) paleontology \\ 
\setlength\parindent{48pt} 4 - oenology, phrenology, ornithology, paleontology \\
\setlength\parindent{24pt}d) glaciology \\
\setlength\parindent{48pt} 5 - oenology, campanology, ichthyology, limnology, glaciology \\
~\\
\setlength\parindent{0pt}5) Using alphabetical order, construct a binary search tree for the words in the sentence "The quick brown fox jumps over the lazy dog." \\
**See attache paper. \\
~\\
\setlength\parindent{0pt}37) Draw the subtree of the game tree for tic-tac-toe beginning at each of these positions.  Determine the value of each of these subtrees. \\
**See attached paper. \\

\end{flushleft}
\end{document}